---
title: "Welcome to Hanchuan Chen's Website"
author: "Hanchuan Chen"
date: "2024-10-29"
output: html_document
---
```{r message=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```


---

## About Me

Hello! My name is **Hanchuan Chen**, and I am a first-year master's student in **Biostatistics**. I am deeply passionate about uncovering insights from data and using statistical methodologies to contribute to advancements in health and science.

## Homework 4

This page is dedicated to **Homework 4**, where I am showcasing my progress and understanding in the field of biostatistics. Here, you'll find my approach, analyses, and reflections on the work I’ve completed as part of my studies. 

## My Passion for Biostatistics

As I continue my journey, I am excited to develop and apply new skills, enhance my analytical thinking, and work on projects that bridge biostatistics and real-world applications. This website serves as a portfolio for my growth, learning, and dedication to biostatistics.

In the navigation bar there is my Resume, also below are three plots shown by using Instacart dataset. Thank you for visiting!

---

```{r scatterplot}
data("ny_noaa")

ny_noaa = 
  ny_noaa |> 
  mutate(year = year(date)) |> 
  mutate(month = month(date)) |> 
  mutate(day = day(date))


ny_noaa |> 
  filter(id == "USW00014743") |> 
  filter(year > 2009) |> 
  plot_ly(
    x = ~snwd, y = ~tmin, type = "scatter", mode = "markers"
  )
```
From this scatterplot, we can see that the snow depth does not have relationship with minimum temperature. Also, scatterplot might not be a good plot to show the relationship between these two variables.

```{r boxplot}
ny_noaa |> 
  filter(id == "USW00014743") |> 
  plot_ly(
    x = ~month, y = ~snwd, type = "box"
  )
```

From this boxplot, it is clear that in the area for this station, snow usually falls between December to March, and the deepest snow depth is in February.  

```{r barplot}
ny_noaa |> 
  filter(id == "USW00014743") |> 
  group_by(year) |> 
  summarize(avg_prcp = mean(prcp, na.rm = TRUE)) |> 
  plot_ly(
    x = ~year, y = ~avg_prcp, type = "bar"
  )
```

By this barplot, we can see the average precipitation in for each year in this specific area. Precipitation in this region has a three-to-four year cycle: the precipitation is normal at first but gradually increase at last. 














